%\begin{flushleft}
\begin{abstract}
The goal of an abstract is to give an overall description of the paper. We should illustrate these points: \\

1)A little background of the problem.

2)Our basic model

3)Our new model, namely what is the improvement of this model compared with those previous ones. Some descriptions about the weakness of previous models(which are what we are trying to solve).

4)The good results we get from our new model.

In general, the abstract must illustrate what we have done in this paper and the significance of these improvements(usually by showing those good results we have).


Understanding the process of information getting around in society network has attracted increasing attention. Information flow in complex society's network is of paramount importance when trying to solve the problem of the spreading of news, whether for analyzing historic events or for future prediction. In the light of the development of social media and social ties, and based on the previous raised models, we bring up a model here so as to represent the society's information spreading process in the network, as well as the historical trend of information network's development. 




The requirement is to build a model to simulate the , with which we have to obtain the following results: build a virtual network to model the spreading of information, and validate it with data from past and now; use it for prediction in year 2050; use the controllable and deterministic factors of information, network topology, links and nodes, to influence and predict the spreading speed and the number of influenced individuals. With more taken into consideration, we obtained more freedom in the model, by far improved the simulation result of real world event, and also coincide with the historical development of social network.



\end{abstract}
