
%======================第一章：问题介绍====================================
\section{Introduction}
%\begin{adjustwidth}{1cm}{0cm}
Understanding process of information getting around society network has attracted increasing attention. Information flow in complex society network is of paramount importance when trying to solve the 


\subsection{literature review}
In previous research, scientists usually base their model on the well know susceptible-infected-recovered ($SIR$) model. The advanced methodology of SIHR \cite{zhao2012sihr}, the further developed SEIQR model\cite{tanaka2015study}, inspired other research of this kind, therefore we can find some relatively mature research like the one by $Linyuan Lv$ and $Duan-Bing Chen$, which we based on to obtain our result. The basic idea of their's is to change the continuous SIR model into a discrete-time model to resemble the spreading of news, and introduce four similar situation of node to 
represent the attitude of people towards news to describe the probalistic spreading of news. $$-------------work in the model part--------------$$

Furthermore, there exist a couple of applications of the model or the variants of it, including the description of growth and decline of network service\cite{tanaka2015study}, predicting forest fire spreading\cite{karafyllidis1997model}. But when taking into consideration the details of the real world society, we find there are still things left to be discussed. 

The nodes, links, and the information itself differs from that of a pure network. 
\begin{itemize}
	\item We can introduce a memory effect to resemble the actual memory loss\cite{zhao2011rumor}.
	\item The information itself, or rather the value of it, determines to which degree people tend to believe it. This is discussed in this paper.
	\item A link may be strong or weak, and the speed of information getting around differs. 
\end{itemize}

The topology structure is distinguished in the following aspects.
\begin{itemize}
	\item The change of link between nodes, namely the dynamic social network decribed in previous work\cite{gerberry2009seiqr}. It represents people making new contacts and lose touch with old friends.
	\item The abidance of $Six Degrees of Separation$\cite{milgram1967small} is missed in previous work during simulation.
	\item The difference of structure entropy, which makes such much difference that the Small World Structure, Random Structure and Regular Structure distinguishes from each other a lot\cite{miritello2011dynamical}. Furthermore, we witness a change of that when taking into account the historical trend of society, which we will discuss in our work.
	\item The connection between the nodes are not to be simply described as non-directional link. Some links are . Data could be collected by crawling the real world network\cite{Kwak:2010:TSN:1772690.1772751}, and we will give it a thorough consideration in this paper. 
\end{itemize}

Despite of the previous research, there are essential points neglected such as the involvement of social media $$something here$$, the change of topology structure and the historical explanation of it, the inherent value of information as mentioned above. 




